analysis

### 2020-01-02 04_Prep_data.Rmd
correct obsolete code

   for (j in unique(dat1$row_spacing)) {
      dat2 <- dat1[dat1$row_spacing == j, ]
      controlY <-
         mean(dat2[dat2$fungicide == "control", "grain_yield.t.ha."])

@@

      dat2[dat2$fungicide == "control", c("yield_gain", "prop_YG")] <-
         NA

@@

slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
              "cluster_1", "cluster_2","cluster_3"
              )] <- "control"

@@

slimmer_PM_dat %>%
   ggplot(aes(y= grain_yield.t.ha, x = vi))+
   geom_point()

>>>>

   for (j in unique(dat1$row_spacing)) {
      dat2 <- dat1[dat1$row_spacing == j, ]
      controlY <-
         mean(dat2[dat2$fungicide_ai == "control", "grain_yield.t.ha."])

@@

      dat2[dat2$fungicide_ai == "control", c("yield_gain", "prop_YG")] <-
         NA

@@

slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
              "cluster_1", "cluster_2","cluster_3"
              )] <- "control"
table(slim_PM_dat$spray_management)
write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)

@@

slimmer_PM_dat %>%
   ggplot(aes(x= grain_yield.t.ha, y = vi))+
   geom_point()

slimmer_PM_dat %>%
   ggplot(aes(x= grain_yield.t.ha, y = Y_Msquare))+
   geom_point()

slimmer_PM_dat[slimmer_PM_dat$vi > 0.5,]

boxplot(PM_MB_means$prop_YG, na.rm = TRUE)

boxplot(PM_MB_means$yield_gain/PM_MB_means$grain_yield.t.ha., main = "Yield loss proportion")
summary(PM_MB_means$yield_gain/PM_MB_means$grain_yield.t.ha., na.rm = TRUE)
unique(PM_MB_means$trial_ref)

boxplot(yield_gain/grain_yield.t.ha. ~ year,data = PM_MB_means, main = "Yield loss proportion")

unique(PM_MB_means$fungicide_ai)
